Experiments

### 2020-11-29 StateOfPractice/Methodology/Experiments.tex
updated modifiability experiment introduction

This experiment is designed to gather qualitative data regarding the modifiability of each software package in a domain. The steps outlined below will result in the creation, by domain experts, of a list of likely changes for software in the domain. This list will then be used to analyze which software packages have been designed to accommodate these expected modifications.

Parnas identifies likely changes as:

 Likely Changes: if the system is required to be easy to change, the requirements should  contain  a  definition  of  the  areas  that  are  considered  likely  to  change.  You  cannot design a system so that everything is equally easy to change. Programmers should not have to decide which changes are most likely\cite{parnas1986rational}

@@

\begin{enumerate}
	\item \textit{Domain Expert}: List all likely changes that a domain expert might make in a software package in the domain.
	\item Using the short list of software packages listed in the  \href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Methodology.pdf}{methodology document}:
	\begin{enumerate}
		\item Identify which of the above changes each package is likely designed to accommodate.
		\item Prepare a short report outlining the likely changes for software in the domain, and which changes each software package is likely designed to accommodate.
	\end{enumerate}
\end{enumerate}

>>>>

This experiment is designed to gather qualitative data regarding the modifiability of each software package. The initial step outlined below produces a list of likely software changes for members of a scientific computing software domain. This list is then used to analyze whether specific software packages have been designed to accommodate these expected modifications.

Parnas's definition of likely changes has informed this analysis: ``If the system is required to be easy to change, the requirements should contain a definition of the areas that are considered likely to change. You cannot design a system so that everything is equally easy to change. Programmers should not have to decide which changes are most likely'' \cite{parnas1986rational}.

@@

\begin{enumerate}
	\item \textit{Domain Expert}: List all likely changes that a domain expert might make in a software package in the domain.
	\item Using the short list of software packages listed in the  \href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Methodology.pdf}{Methodology document}:
	\begin{enumerate}
		\item Identify which of the above changes each package is likely designed to accommodate.
		\item Prepare a short report outlining the likely changes for software in the domain, and which changes each software package is likely designed to accommodate.
	\end{enumerate}
\end{enumerate}
